Methods that remove batch effects while retaining group differences may lead to exaggerated confidence in downstream analyses

### 2014-11-17 tex/manuscript.tex
Minor updates

A one-way ANOVA checking for group differences will assume that the $F$-statistic follows an $\text{F}_{q,n-q-1}$ distribution. However, if the data have been batch adjusted prior to this analysis, the approximate distribution of this $F$-statistic, with correct first two momenta, will be
\begin{equation}
F\approx\frac{\tilde q\tilde\sigma^2}{q\sigma^2}\cdot\left(1+\frac{r}{n-q-r-1}\right)\cdot\text{F}_{\tilde q,n-q-r-1}
\end{equation}
where $\tilde q$ and $\tilde\sigma^2$ are as computed in the appendix and satisfy $\tilde q\tilde\sigma^2\ge q\sigma^2$ and $\tilde q\le q$ with equalities if and only if the groups are perfectly balanced between the batches.

@@

We would like to express $\tilde\sigma^2$ and $\tilde q$ terms of the original design matrices. The rotated design matrices were defined as $B_0=BU_0$, etc., using the rotation $U=[U_0\mid U']$ so that $AU_0=0$ while $AU'$ is non-singular. Hence, it follows that $V_0V_0^t=\rho_A=1-A^t(AA^t)^{-1}A$ which is the projection onto the $n-p$-hyperplane perpendicular to the $p$-hyperplane spanned by $A$. This allows us to express
\begin{equation}
L_0=U_0^tLU_0
\quad\text{where}\quad
L=
\end{equation}

>>>>

A one-way ANOVA checking for group differences will assume that the $F$-statistic follows an $\text{F}_{q,n-q-1}$ distribution. However, if the data have been batch adjusted prior to this analysis, the approximate distribution of this $F$-statistic, with correct first two momenta, will be
\begin{equation}
F\approx\frac{\tilde q\tilde\sigma^2}{q\sigma^2}\cdot\left(1+\frac{r}{n-q-r-1}\right)\cdot\text{F}_{\tilde q,n-q-r-1}
\end{equation}
where $\tilde q$ and $\tilde\sigma^2$ are as computed in the appendix and satisfy $\tilde q\tilde\sigma^2\ge q\sigma^2$ and $\tilde q\le q$ with equalities if and only if the groups are evenly represented in all batches.

@@

We would like to express $\tilde\sigma^2$ and $\tilde q$ terms of the original design matrices. The rotated design matrices were defined as $B_0=BU_0$, etc., using the rotation $U=[U_0\mid U']$ so that $AU_0=0$ while $AU'$ is non-singular. Hence, it follows that $V_0V_0^t=\rho_A=1-A^t(AA^t)^{-1}A$ which is the projection onto the $n-p$-hyperplane perpendicular to the $p$-hyperplane spanned by $A$. This allows us to express
\begin{equation}
L_0=U_0^tLU_0
\quad\text{where}\quad
L=
\end{equation}
\NB{Need to complete this part...}
